\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-07-19 analysis/paper/paper.Rmd
to change ggtheme, simply change paper_gg_theme object defined in first chunck
then all the figures will update to that theme

echo_plot_code <- TRUE
```

@@

```{r plot-stratified-erspc-data, eval = eval_cs1, echo = FALSE, fig.width=7, fig.height=5, fig.asp=0.75, fig.cap="Population time plot for ERSPC data."}
plot(pt_object, 
     add.base.series = TRUE,
     ratio = 0.7,
     facet.params = list(ncol = 2),
     ribbon.params = list(fill = "gray50"),
     case.params = list(size = 0.8),
     base.params = list(size = 0.8)) + theme_bw(base_size = 10) + theme(legend.position = "bottom") + 
  scale_y_continuous(labels = scales::label_number_si())
```

@@

plot(popTimeData, 
     add.competing.event = TRUE,
     comprisk = TRUE,
     # add.base.series = TRUE,
     # ratio = 0.7,
     # facet.params = list(ncol = 2),
     ribbon.params = list(fill = "gray50"),
     case.params = list(size = 0.8),
     competing.params = list(size = 0.8)) + 
  theme_bw(base_size = 10) + 
  theme(legend.position = "bottom") + 
  scale_y_continuous(labels = scales::label_number_si())

@@

ggplot(risk_all, aes(x = Time, y = Risk, colour = Method)) +
  # geom_line for smooth curve
  geom_line(data = dplyr::filter(risk_all, Method == "Case-base")) +
  # geom_step for step function
  geom_step(data = dplyr::filter(risk_all, Method != "Case-base")) +
  facet_grid(Disease ~ .) +
  ylim(c(0, 1)) +
  theme_bw(base_size = 10) + 
  theme(legend.position = "bottom") +
  xlab("Time (in Months)") +
  ylab("Relapse risk")
```

@@

```{r baselines, echo=FALSE, eval=eval_cs3}
cox_ci <- ggplot(baseCoxComparisonData, aes(Time)) +
  geom_line(aes(y = APS, colour = "APS"), lwd = 1) +
  geom_line(aes(y = Full, col = "Full"), lwd = 1) +
  geom_line(aes(y = SPS, colour = "SPS"), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M")) + theme_bw(base_size = 10) + theme(legend.position = "bottom")
```

@@

cox_brier <- ggplot(data = brierPlotter, mapping = aes(x = times, y = brierScore, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  labs(color = "Models") +
  # ggtitle("Brier scores over time") +
  scale_color_manual(values = q4[1:3]) + theme_bw(base_size = 10)

@@

lolliplotDots <- lolliplotDots[-which(is.na(lolliplotDots$estimate)), ]
dwplot(lolliplotDots) +
  theme(
    axis.text.y = element_text(size = 11, angle = 0, hjust = 1, vjust = 0),
    strip.text.x = element_blank(),
    strip.background = element_rect(colour = "white", fill = "white"),
    legend.position = c(.855, 0.15), legend.text = element_text(size = 11)
  ) +
  theme_bw(base_size = 10) + 
  theme(legend.position = "bottom") + 
  # ggtitle("Coefficient plot") +
  labs(color = "Models") +
  scale_color_manual(values = q4[1:3])
```

@@

```{r cs3Final, echo=FALSE, eval=eval_cs3}
reg_ci <- ggplot(ab, aes(Time)) +
  geom_line(data = baseCoxComparisonData, mapping = aes(y = Full, colour = "Cox"), lwd = 1) +
  geom_line(aes(y = absRisk, colour = Model), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  # ggtitle("Absolute risk curves") +
  scale_color_manual(values = q4, breaks = c("Cox", "Penalized Cox", "Penalized logistic", "K-M")) + 
  theme_bw(base_size = 10) + 
  theme(legend.position = "bottom")
```

@@

reg_brier <- ggplot(data = data_brier, mapping = aes(x = times, y = Brier, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  # ggtitle("Brier score over time") +
  labs(color = "Models") +
  theme_bw(base_size = 10) + 
  theme(legend.position = "bottom")+
  scale_color_manual(values = q4)

@@

stanford_popTime <- popTime(jasa,
  time = "futime",
  event = "fustat"
)
plot(stanford_popTime,
     ribbon.params = list(fill = "grey50")) + theme_bw(base_size = 10) + theme(legend.position = "bottom") 
```

@@

ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
  geom_line() +
  theme_minimal() +
  theme(legend.position = "top") +
  ylab("Hazard") +
  xlab("Follow-up time")
```

@@

plot(absrisk,
     id.names = c("NoTrans","Trans")) + theme_bw(base_size = 10) + theme(legend.position = "bottom")

@@

```{r stanford-1y-haz, eval = eval_cs4}
# Compute hazards---
# First, create a list of time points for both exposure status
one_yr_haz <- data.frame(futime = seq(0, 365,
  length.out = 100
))
one_yr_haz <- mutate(one_yr_haz,
  offset = 0,
  exposure = if_else(futime < 30, 0, 1)
)
one_yr_haz$hazard <- exp(predict(fit4,
  newdata = one_yr_haz,
  type = "link"
))
ggplot(one_yr_haz, aes(futime, hazard)) +
  geom_line() +
  theme_minimal() +
  theme(legend.position = "top") +
  ylab("Hazard") +
  xlab("Follow-up time") +
  geom_vline(xintercept = 30, linetype = "dashed")
```

>>>>

echo_plot_code <- TRUE

paper_gg_theme <- theme_bw(base_size = 10) + theme(legend.position = "bottom")
```

@@

```{r plot-stratified-erspc-data, eval = eval_cs1, echo = FALSE, fig.width=7, fig.height=5, fig.asp=0.75, fig.cap="Population time plot for ERSPC data."}
plot(pt_object, 
     add.base.series = TRUE,
     ratio = 0.7,
     facet.params = list(ncol = 2),
     ribbon.params = list(fill = "gray50"),
     case.params = list(size = 0.8),
     base.params = list(size = 0.8)) + 
  paper_gg_theme +  
  scale_y_continuous(labels = scales::label_number_si())
```

@@

plot(popTimeData, 
     add.competing.event = TRUE,
     comprisk = TRUE,
     # add.base.series = TRUE,
     # ratio = 0.7,
     # facet.params = list(ncol = 2),
     ribbon.params = list(fill = "gray50"),
     case.params = list(size = 0.8),
     competing.params = list(size = 0.8)) + 
  paper_gg_theme +  
  scale_y_continuous(labels = scales::label_number_si())

@@

ggplot(risk_all, aes(x = Time, y = Risk, colour = Method)) +
  # geom_line for smooth curve
  geom_line(data = dplyr::filter(risk_all, Method == "Case-base")) +
  # geom_step for step function
  geom_step(data = dplyr::filter(risk_all, Method != "Case-base")) +
  facet_grid(Disease ~ .) +
  ylim(c(0, 1)) +
  paper_gg_theme +  
  xlab("Time (in Months)") +
  ylab("Relapse risk")
```

@@

```{r baselines, echo=FALSE, eval=eval_cs3}
cox_ci <- ggplot(baseCoxComparisonData, aes(Time)) +
  geom_line(aes(y = APS, colour = "APS"), lwd = 1) +
  geom_line(aes(y = Full, col = "Full"), lwd = 1) +
  geom_line(aes(y = SPS, colour = "SPS"), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M")) + 
  paper_gg_theme
```

@@

cox_brier <- ggplot(data = brierPlotter, mapping = aes(x = times, y = brierScore, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  labs(color = "Models") +
  # ggtitle("Brier scores over time") +
  scale_color_manual(values = q4[1:3]) + 
  paper_gg_theme

@@

lolliplotDots <- lolliplotDots[-which(is.na(lolliplotDots$estimate)), ]
dwplot(lolliplotDots) +
  theme(
    axis.text.y = element_text(size = 11, angle = 0, hjust = 1, vjust = 0),
    strip.text.x = element_blank(),
    strip.background = element_rect(colour = "white", fill = "white"),
    legend.position = c(.855, 0.15), legend.text = element_text(size = 11)
  ) +
  paper_gg_theme +  
  # ggtitle("Coefficient plot") +
  labs(color = "Models") +
  scale_color_manual(values = q4[1:3])
```

@@

```{r cs3Final, echo=FALSE, eval=eval_cs3}
reg_ci <- ggplot(ab, aes(Time)) +
  geom_line(data = baseCoxComparisonData, mapping = aes(y = Full, colour = "Cox"), lwd = 1) +
  geom_line(aes(y = absRisk, colour = Model), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  # ggtitle("Absolute risk curves") +
  scale_color_manual(values = q4, breaks = c("Cox", "Penalized Cox", "Penalized logistic", "K-M")) + 
  paper_gg_theme
```

@@

reg_brier <- ggplot(data = data_brier, mapping = aes(x = times, y = Brier, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  # ggtitle("Brier score over time") +
  labs(color = "Models") +
  paper_gg_theme +  
  scale_color_manual(values = q4)

@@

stanford_popTime <- popTime(jasa,
  time = "futime",
  event = "fustat"
)
plot(stanford_popTime,
     ribbon.params = list(fill = "grey50")) + 
  paper_gg_theme
```

@@

ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
  geom_line() +
  paper_gg_theme +  
  ylab("Hazard") +
  xlab("Follow-up time")
```

@@

plot(absrisk,
     id.names = c("NoTrans","Trans")) + 
  paper_gg_theme

@@

```{r stanford-1y-haz, eval = eval_cs4}
# Compute hazards---
# First, create a list of time points for both exposure status
one_yr_haz <- data.frame(futime = seq(0, 365,
  length.out = 100
))
one_yr_haz <- mutate(one_yr_haz,
  offset = 0,
  exposure = if_else(futime < 30, 0, 1)
)
one_yr_haz$hazard <- exp(predict(fit4,
  newdata = one_yr_haz,
  type = "link"
))
ggplot(one_yr_haz, aes(futime, hazard)) +
  geom_line() +
  paper_gg_theme +  
  ylab("Hazard") +
  xlab("Follow-up time") +
  geom_vline(xintercept = 30, linetype = "dashed")
```
